PAMELA: an annotation-based Java Modeling Framework

### 2021-02-12 architecture.tex
Adding response letter template

\subsection{Installation}
\label{sub:installation}

\todo{Maybe a word on how to install.}

@@

Programmers may already reuse a number of advanced programming features
(some already mentioned) such as: multiple inheritance and traits, containment
management, cloning, fine-grained notifications management, object graph
comparison and diff/merge, visiting patterns, clipboard management, validation,
support for \emph{design by contract} by integrating assertions from Java
Modeling Language (JML), Metaprogramming, Aspect Oriented Programming. Each of
those features is described on a dedicated page that is reachable from the
official web site\footnote{\url{https://pamela.openflexo.org/SNAPSHOT/}}.
Experimented programmers may extend PAMELA defining new annotations.

>>>>

%\subsection{Installation}
%\label{sub:installation}

%\todo{Maybe a word on how to install.}
% We decided not to do it

@@

Programmers may already reuse a number of advanced programming features
(some already mentioned) such as: multiple inheritance and traits, containment
management, cloning, fine-grained notifications management, object graph
comparison and diff/merge, visiting patterns, clipboard management, validation,
support for \emph{design by contract} by integrating assertions from Java
Modeling Language (JML), Metaprogramming, Aspect Oriented Programming. Each of
those features is described on a dedicated page that is reachable from the
official web site\footnote{\url{https://pamela.openflexo.org}}.
Experimented programmers may extend PAMELA defining new annotations.
